=======
---
title: "**Table development starter**"
geometry: "left=0.75in,right=0.75in,top=1in,bottom=1in"
output:
  bookdown::pdf_document2:
    toc: no
    number_sections: false
urlcolor: blue
documentclass: article
header-includes:
    - \usepackage{setspace}\onehalfspacing
    - \usepackage{float}
    - \usepackage{fancyhdr}
    - \pagestyle{fancy}
fontsize: 12pt
sansfont: Calibri
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
knitr::opts_chunk$set(fig.pos = "H", out.extra = "")
library(tidyverse, quietly=T, verbose=F)
library(knitr, quietly=T, verbose=F)
library(kableExtra, quietly=T, verbose=F)
library(marmap, quietly=T, verbose=F)
library(sf, quietly=T,verbose=F)
data("iris")
iris <- head(iris,5)
```

```{r loadMarmapBathy}
# # Pull NOAA bathymetry data, you must provide the latitude/longitude bounds and a resolution (higher resolutions take more time to process)
# Bathy <- getNOAA.bathy(lon1 = -75, lon2 = -62,
#                        lat1 = 39, lat2 = 48, resolution = 1)
# 
# # Now do a bit of data wrangling so we can plot it:
# # Convert data to matrix
# Bathy_Final <- as.matrix(Bathy)
# class(Bathy_Final) <- "matrix"
# 
# # Now reshape it to long format and plot
# BathyData <- Bathy_Final %>%
#   as.data.frame() %>% # Convert the matrix to a data.frame
#   rownames_to_column(var = "lon") %>% # Switch to long format
#   gather(lat, value, -1) %>%
#   mutate_all(funs(as.numeric)) # Make everything a number

# marmap isn't working on my computer so:
BathyData <- read_rds(paste0(getwd(), "/Data/BathymetryData.RDS"))
```

```{r PlotMarmapBathy}
ggplot() +
  geom_contour_filled(data = BathyData, aes(x = lon, y = lat, z = value),
                      breaks = c(0, -50, -100, -200, -300, -400, -500, -5000)) + # Specify custom bathymetric lines to keep
  xlab("Longitude") + # Update axis labels
  ylab("Latitude") +
  scale_fill_manual(values =  c("#DEF5E5FF", "#A0DFB9FF", "#54C9ADFF", "#38AAACFF", "#348AA6FF", "#366A9FFF", "#40498EFF"), name = "Depth (m)", labels = c("[0,50)", "[50,100)", "[100, 200)", "[200, 300)", "[300,400)", "[400,500)", "[500,5000)" )) + # Pick specific colors and label them to match the bathymetric lines so we end up with a nice legend and colors
  coord_sf(xlim = c(-74, -64),  ylim = c(40, 47.3)) + # Trim the map dimensions a bit and fix the horizontal stretch. !!! Change this if you want to zoom in/out on a specific area
  theme_void() + # Change the background theme, there are lots of options to explore
  theme(panel.background=element_rect(fill="gray"), legend.position = "none")

```
```{r loadSurveyData}
# Load
survey_data <- read.csv((paste0(getwd(), "/Data/Survey_Data.csv")))

# Subset to NEFSC BTS WGOM
survey_data <- subset(survey_data, SURVEY=="NEFSC BTS")
survey_data <- subset(survey_data, STOCK=="WGOM")

# Conver to sf object
surveys_sf <- st_as_sf(survey_data, coords=c("LON", "LAT"),
                       na.fail=T)

# Set coordinat ref system (unprojected WGS84)
st_crs(surveys_sf) <- "EPSG: 4326"
```


```{r plotBathySurvey}
# Plot survey points over bathymetry
pointsplot <- ggplot() +
  geom_contour_filled(data = BathyData, aes(x = lon, y = lat, z = value),
                      breaks = c(0, -50, -100, -200, -300, -400, -500, -5000)) + # Specify custom bathymetric lines to keep
  geom_sf(data=surveys_sf, pch='x', col="black", cex=1, alpha=0.5) +
  #xlim(st_bbox(surveys_sf)[1], st_bbox(surveys_sf)[3]) +
  #ylim(st_bbox(surveys_sf)[2], st_bbox(surveys_sf)[4]) +
  xlab("Longitude") + # Update axis labels
  ylab("Latitude") +
  scale_fill_manual(values =  c("#DEF5E5FF", "#A0DFB9FF", "#54C9ADFF", "#38AAACFF", "#348AA6FF", "#366A9FFF", "#40498EFF"), name = "Depth (m)", labels = c("[0,50)", "[50,100)", "[100, 200)", "[200, 300)", "[300,400)", "[400,500)", "[500,5000)" )) + # Pick specific colors and label them to match the bathymetric lines so we end up with a nice legend and colors
  coord_sf(xlim = c(-71, -66.0),  ylim = c(40.0, 44.5)) + # Trim the map dimensions a bit and fix the horizontal stretch. !!! Change this if you want to zoom in/out on a specific area
  theme_void() + # Change the background theme, there are lots of options to explore
  theme(panel.background=element_rect(fill="gray"), legend.position = "none")

plot(pointsplot)
```

```{r extraPic}
iris %>% 
  mutate_at(vars(Petal.Length), 
            funs(factor)) %>% 
  mutate(Picture=" ") %>% 
  kable(
    caption = "Add picture",
    booktabs=TRUE,
    align="cccccc"
    ) %>%
  kableExtra::kable_styling(
      latex_options ="HOLD_position"
    )%>% 
  row_spec(0, background="darkgray", color="white") %>% 
  pack_rows(index = c("1.3" = 1, "1.4" = 3, "1.5" = 1),
            background="gray!10",
            hline_before=T, hline_after = T,
            latex_align = "c") %>% 
  #column_spec(6, image = "jigging_substrate_rs.png") %>% 
  column_spec(1:6,
              width = c(rep("0.75in",5), "1in"),
              latex_valign = "m")
```

Try using gt for plot - this lets you add a ggplot into a table but I haven't tested to see if you can add tooltips
```{r}
library("gt")
dplyr::tibble(column1 = "trawl data", map = NA) %>% # Placeholder tibble with NA for map
  gt() %>% # Turn tibble into gt table
  text_transform(
    locations = cells_body(columns = map), # Turn map object into ggplot image
    fn = function(x){
      MAP %>% ggplot_image(height = px(200))
    }
  )
  
```
